The Aquarius Stream Progenitor Was Not A Globular Cluster: \\ Its History Could Be Far More Interesting\altaffilmark{1}

### 2013-01-01 2012-aqs/draft-aqs.tex
Fixed changes made on paper

\author{Andrew R. Casey\altaffilmark{2,3} and distinguished collaborators}
\altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observa- tory, Chile.}
\altaffiltext{2}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; acasey@mso.anu.edu.au}
\altaffiltext{3}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\begin{abstract}
We present a detailed dynamic and chemical analysis of 5 Aquarius stream giants observed using the MIKE spectrograph on the Magellan Clay Telescope. 
\end{abstract}

@@

\section{Introduction}

Stellar streams arise from tidal effects as satellite systems infall onto the Milky Way. The phase space information of stars within such streams are sensitive to the galactic potential. Therefore, they can collectively constrain the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way. Moreover, individual elemental abundances for stars within these streams help unravel the chemical evolution of the Galaxy. 
% Consider adding a final sentence about the amount of work that has gone into stellar streaams

Wide-field surveys have proved excellent sources for finding galactic substructures, including stellar streams. Dozens of streams reaching out up to 150\,kpc in the halo have been identified through photometric selections and matched-filtering techniques \citep{belokurov;et-al_2007,koposov_SG1}. However, as \citet{helmi;white_1999} point out, these approaches are only successful for identifying substructures that are sufficiently distant from the solar neighbourhood. A nearby stream within $\sim{}$10\,kpc will not appear as an on-sky over-density, as the stars would be sparsely positioned across the sky. Such substructures would only be detectable with kinematic, or perhaps precise chemical information.

% Talk about RAVE
It is therefore necessary to survey solar neighbourhood stars with spectroscopy in order to detect any nearby substructures. The RAVE (Radial Velocity Experiment) began such a survey in 2003 and has observed spectra from over 500,000 stars across 17,000 deg$^{2}$. As the name suggests, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond. In an attempt to remain kinematically unbiased, RAVE candidates were selected based only on their apparent magnitude. With the exception of bulge stars where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed. Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient S/N, estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.

% Identification of the aquarius stream
Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5 \lesssim d \lesssim 10$\,kpc) stars in the vicinity of the Aquarius constellation $(l, b) = (60\,^\circ, -55\,^\circ)$. The artefact is most apparent when examining kinematics against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$. \citet{williams;et-al_2011} employed a selection criteria of $-250 < V_{HEL} < -150$\,km s$^{-1}$, $30\,^\circ < l < 75\,^\circ, J > 10.3$ to maximize the contrast between the stream and halo background, identifying 15 stream candidates in the process. The average heliocentric radial velocity of these members was found to be $V_{HEL} = -199$\,km s$^{-1}$, with a dispersion of 27\,km s$^{-1}$. The radial velocities outputted by the RAVE survey are described to be $\sim2$\,km s$^{-1}$, so the wide kinematic distribution appears to be real.

%When compared to other streams identified in the halo, this is an unusually wide kinematic dispersion. Streams are generally considered to be kinematically cold, with dispersions of $\sigma_v < 8$\,km s$^{-1}$.

% QUANTIFYING THE STREAM DETECTION
Upon examining the galactic longitude and radial velocities of Aquarius stars, the stream appears quite distinct from the halo. In order to quantify the statistical likelihood that the Aquarius stream is a true substructure, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy models. Predicted particles and observed stars between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{hel}}$ using varying grid cell sizes between $25-70\,^\circ$ and 20-100\,km s$^{-1}$ respectively. The significance of the stream is calculated for each cell. \citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the grid cell sizes employed for the Besan\c{c}on model. By sampling the Galaxia model multiple times with varying extinction models, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level. Given the high-latitude of the stream and proximity of the stream, it is not surprising that dust had a negligible effect on the overall significance. \citet{williams;et-al_2011} concluded that the over-density in $l, V_{hel}$ is a true substructure, and neither the choice of galaxy model, cell size, nor the extinction model made any real difference to the stream detection significance.

@@

Given the extent of stellar debris the Sagittarius dwarf has littered throughout the Milky Way, it is reasonable to suspect the Aquarius stream might originate from the Sagittarius dwarf. Indeed, the Aquarius stream stars do not lie far from the orbital plane of Sagittarius and the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the Sagittarius stream. However, \citet{williams;et-al_2011} found the Aquarius $XYZ$ positions and kinematics (specifically $V_{Z}$ and $V_\phi$) are quite distinct from Sagittarius. Based on the phase space information available, \citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo over-densities.

The Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance. The dispersion in the stream's metallicity has yet to be fully characterised. \citet{williams;et-al_2011} found the stream to have an average of $\mbox{[M/H]} = -1.0 \pm 0.4$, compared to $\mbox{[M/H]} = -1.1 \pm 0.6$ for background stars after the same selection cuts had been employed. Of the 12 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range is wide: between --2.02 and --0.33 dex. Spectroscopic observations of higher resolution and S/N are necessary to accurately determine the metallicity distribution function. To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($R = 25,000$) spectra with modest S/N ($\sim$30 pixel$^{-1}$) for six Aquarius stream giants. Their data indicated a much narrower metallicity distribution: $\mbox{[Fe/H]} = -1.09 \pm 0.10$\,dex extending between $\mbox{[Fe/H]} = -1.25$ to $-0.98$\,dex; the level of negligible intrinsic chemical scatter which is typically observed in globular clusters. The largest [Fe/H] discrepancy between the two studies was $\Delta\mbox{[Fe/H]} = -0.66$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample. The most metal-poor star in the \citet{williams;et-al_2011} study was not observed by \citet{wylie-de-boer;et-al_2012}.

%The chemical coherence in the \citet{wylie-de-boer;et-al_2012} study is most intriguing.

In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured light element abundances for the Aquarius stream stars -- the only study to do so until now. Primarily they focussed on Na, O, Ni, Mg, and Al abundances. Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars. Most notably, an anti-correlation in sodium and oxygen abundance has been identified in all well-studied globular clusters to date. Originally this was thought to arise from internal mixing along the giant branch. However, dwarf stars were found to exhibit strong Na-enhancement and O-depletions, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing. It is well known now that photospheric abundance variations resulting from internal mixing are limited to C, N and Li. The Na-O pattern provides the best evidence that stars have formed in a globular cluster environment and that their chemical enrichment history has been dominated by Sn II events. From high-resolution spectroscopy of five stars in Aquarius, four of which had Na, O measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios for halo stars of the same metallicity. No strong oxygen depletion was evident in their stars.

There are other abundances patterns that allow us to infer the chemical evolution of a given cluster. \citet{nissen;schuster_1997} first noted that only the distant solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe]. \citet{fulbright_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient. If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{nissen;schuster_1997} proposed that this chemical trend may be indicative of the halo merger history. Although there are some caveats to this chemical pattern (see \S\ref{sec:ni-na-relation}), at the very least the Na-Ni correlation may provide an indication whether stars became chemically enriched in dSph-like environments. \citet{wylie-de-boer;et-al_2012} found all their Aquarius stars to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dSph satellite.

Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream must be the result of a tidally disrupted globular cluster. \citet{williams;et-al_2011} had previously precluded this possibility after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{hel}$ with known, nearby globular clusters of similar metallicities. However, no known globular cluster could match their simulation.

We seek to investigate the nature of the Aquarius stream, in particular the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}. We present a detailed analysis for five confirmed Aquarius stream members from high-resolution, high S/N observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} on the Magellan Clay telescope. Our analysis includes determining the galactic dynamics and orbital paths for the Aquarius stream, and measuring precise chemical abundances. Details of the observations and data reduction are outlined in the following section. The data analysis is chronicalled in \S\ref{sec:analysis} and a detailed discussion of these results resides in \S\ref{sec:discussion}. In \S\ref{sec:conclusion} we present our conclusions and critical interpretations.

\clearpage
\section{Observations \& Data Reduction}

The most comprehensive sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}. Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional star from the original \citet{williams;et-al_2011} sample. The additional star, J2306265-085103, had insufficient S/N in the RAVE sample for stellar parameters to be accurately determined. Program stars were observed in July 2011 in good seeing at high airmass (Table \ref{tab:observations}), and X standard stars were observed as part of a separate program in March 2011. All observations were taken using the 1.0'' slit, providing a spectral resolution of $R = 28,000$. The exposure times for our program stars varied per star from X-Y seconds to ensure a Signal-to-Noise ratio (S/N) in excess of 100 per pixel element at 600 nm.

Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration. The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}. One of our standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}. The resultant spectra from both reduction workflows were compared for residual fringing, S/N, and wavelength calibration. No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of our reductions. Each reduced echelle order was carefully normalised using a third order spline. Normalised orders  for a given star were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.

The white dwarf HR 6141 was observed on X with a S/N of 400 pixel$^{-1}$ to account for telluric absorption. The S/N for HR 6141 exceeds the S/N in any of our program stars. Although the atmospheric conditions are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption. Critical transitions necessary for abundance analyses that are affected by the earth's atmosphere are later corrected for telluric absorption (see \S\ref{sec:telluric-absorption}), but great attention is paid to telluric band-heads at X and X such that we are not over- or under-correcting the atmospheric absorption.

@@

@@

\subsection{Radial Velocities}
\label{sec:radial-velocities}
The radial velocity for each star was determined in a two-step method. An initial estimate of the radial velocity was ascertained by cross-correlation with the synthetic spectrum of a giant with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}. The observed spectrum was shifted to the pseudo-rest frame using this initial velocity. Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.

With our spectrum at near-rest, we measured the equivalent widths of $\sim$200 lines by fitting Gaussian functions to the absorption profiles. Fitted Gaussian profiles provides us with a measured equivalent width, the full-width half-maximum of the profile, and the central wavelength. Thus, the residual radial velocity can be found from the ratio of the central and rest line wavelengths. The final radial velocity for the star is provided by the mean of these $\sim$200 line velocity measurements. Figure \ref{fig:line-velocities} shows the line velocities for HD41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$. As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and our standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements. This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$. This process was performed for all observations. The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method. Heliocentric velocities agree quite well with the \citet{williams;et-al_2011} published values: $\langle\Delta{V_{hel}}\rangle = 2.8$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published by the RAVE survey.

@@

For the measurement of atomic absorption lines, we employed the line list of \citet{yong;et-al_2005} with additional transitions of Cr, Sc, Zn, and Sr from \citet{frebel;et-al_2010}. We supplemented the list with hyperfine-structure data for Sc and Mn from the Kurucz compilation \citet{kurucz;1998}. Molecular line data for CH was taken from \citet{plez;et-al_2008,plez;et-al_2009}. For lines with hyperfine structure, blended transitions or molecular features, we determined the transition abundance using a spectral synthesis approach where the abundance of a given species is found by by matching a synthetic spectrum to the observed spectrum. Equivalent widths were measured to determine the abundances of all other transitions.

The equivalent widths for all absorption lines were measured automatically using software written for this study. Given the rest wavelength and an initial guess of the full-width half-maxium (FWHM), a Gaussian function is iteratively fitted to the absorption profile. At the same time, the local continuum is found within 20\,\AA{} either side of the rest wavelength using a second-order polynomial. Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements. Any group of pixels that deviate significantly ($>$2-$\sigma$) from the local continuum are either persistent cosmic ray hits, or trough points of a neighbouring absorption profile. We attempt to fit a Gaussian profile to each group of deviating pixels, using the current best estimate for the local continuum. If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, then all points belonging to that profile are excluded from the continuum determination. When fitting Gaussian profiles, the $\chi^2$ difference between the observation and the profile is minimized. In order to account for crowded absorption regions where the $\chi^2$ value might be influenced by a nearby profile, our $\chi^2$ function is weighted based on the distance to the rest wavelength by the function

@@

\noindent where $\lambda_{r}$ (rest wavelength) and $\sigma$ are free parameters during the iterative fitting process. As a consequence of Eq. \ref{eq:chi-weight}, pixels near the rest wavelength are weighted higher than those on the wings, forcing the fit to disregard blended or crowded regions. Although this approach relies on a reasonably accurate radial velocity correction ($<$4\,km s$^{-1}$; which is easily achieved), it greatly improves the accuracy of the equivalent width measurements.

The results of our iterative fitting approach are completely \textit{insensitive} to the initial FWHM guess. Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- unphysically large values for high-resolution spectra -- does not alter either the FWHM or the equivalent width for any of our measurements. Only a small increase in computational cost is observed. Although we are extremely confident in our automatic equivalent width measurements, every absorption profile was examined by eye for quality, and spurious measurements were excluded.

>>>>

\author{Andrew R. Casey\altaffilmark{2,3} and distinguished collaborators}
\altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
\altaffiltext{2}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; acasey@mso.anu.edu.au}
\altaffiltext{3}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\begin{abstract}
We present a detailed dynamic and chemical analysis of 5 Aquarius stream giants observed using the MIKE spectrograph on the Magellan Clay Telescope. Assuming all candidates are stream members, our data indicate the Aquarius stream has a large metallicity dispersion. We find no Na-O anti-correlation, and no chemical evidence that the stream is a result of a disrupted globular cluster, contrary to \citet{wylie-de-boer;et-al_2012}.

\end{abstract}

@@

\section{Introduction}
Galaxies are formed hierarchically through chaotic mergers of smaller systems. The Milky Way is no exception. In our own stellar  halo, we see ongoing evidence of these accretion events. As accreting satellites infall onto the galaxy, tidal forces disrupt the dwarf, hurtling stars in leading and trailing streams. The phase space information of stars within such streams are sensitive to the galactic potential. They can collectively constrain the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way. Moreover, individual chemical abundances can constrain the  precise nucleosynthesis sites where elements are forged, and can collectively trace the chemical evolution of the galaxy.

% Consider adding a final sentence about the amount of work that has gone into stellar streaams

Wide-field surveys have proved excellent sources for finding stellar streams. Dozens of streams reaching out up to 150\,kpc in the halo have been identified through photometric selections and matched-filtering techniques \citep{belokurov;et-al_2007,koposov_SG1}. Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion. However, as \citet{helmi;white_1999} point out, these observing strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood. A nearby stream, within $\sim{}$10\,kpc, will not appear as an on-sky over-density, as the stars would be sparsely positioned across the sky. Such substructures would only be detectable by their kinematics, or perhaps precise chemical abundances through a `chemical tagging' approach (e.g. see \citet{freeman;bland-hawthorn_2003}).

% Talk about RAVE
It is therefore necessary to survey solar neighbourhood stars with spectroscopy in order to detect any nearby substructures. The RAVE (Radial Velocity Experiment) began such a survey in 2003 and has observed spectra from over 500,000 stars across 17,000 deg$^{2}$. As the name suggests, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond. In an attempt to remain kinematically unbiased, RAVE candidates were selected based only on their apparent magnitude. With the exception of bulge stars, where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed. Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient S/N, estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.

% Identification of the aquarius stream
Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5 \lesssim d \lesssim 10$\,kpc) stars in the vicinity of the Aquarius constellation $(l, b) = (60\,^\circ, -55\,^\circ)$. Thus, the co-moving group was named the Aquarius stream. The stream is most apparent when examining velocities against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$. \citet{williams;et-al_2011} employed a selection criteria of $-250 < V_{HEL} < -150$\,km s$^{-1}$, $30\,^\circ < l < 75\,^\circ$ and $J > 10.3$ to maximize the contrast between the stream and background, identifying 15 candidates in the process. The average heliocentric velocity of these members was found to be $V_{HEL} = -199$\,km s$^{-1}$, with a dispersion of 27\,km s$^{-1}$. The radial velocities outputted by the RAVE survey are described to be $\sim2$\,km s$^{-1}$, so the wide kinematic distribution appears to be real.

% QUANTIFYING THE STREAM DETECTION
Upon examining the galactic longitude and velocities of Aquarius stars, the stream appears quite distinct from the halo. In order to quantify the statistical likelihood that the Aquarius stream is truly distinct from the halo, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy simulations. The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{hel}}$ using varying grid cell sizes between $25-70\,^\circ$ and 20-100\,km s$^{-1}$ respectively. The RAVE sample was binned in the same way, and the statistical significance of the over-density is calculated for each cell. \citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the grid cell sizes employed for the Besan\c{c}on model. By sampling the Galaxia model multiple times with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level or higher. Given the high-latitude and proximity of the stream, it is not surprising that dust had a negligible effect on the statistical significance. \citet{williams;et-al_2011} concluded that the over-density in $l, V_{hel}$ is a true substructure, and neither the choice of galaxy model, cell size, nor the extinction model made any real difference to the stream detection significance.

@@

Given the extent of stellar debris the Sagittarius dwarf has littered throughout the Milky Way, it is reasonable to suspect the Aquarius stream might originate from the Sagittarius dwarf. Indeed, the Aquarius stream stars do not lie far from the orbital plane of Sagittarius and the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the Sagittarius stream. However, \citet{williams;et-al_2011} found the Aquarius space positions and kinematics (specifically $V_{Z}$ and $V_\phi$) are quite distinct from Sagittarius. Based on the phase space information available, \citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo over-densities.

The Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$ \citep{williams;et-al_2011}, slightly more metal-rich than halo stars at the same distance. The dispersion in the stream's metallicity has yet to be fully characterised. \citet{williams;et-al_2011} found the stream to have an average of $\mbox{[M/H]} = -1.0 \pm 0.4$, compared to $\mbox{[M/H]} = -1.1 \pm 0.6$ for background stars after the same selection cuts had been employed. Of the 12 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range is wide: between --2.02 and --0.33 dex. Spectroscopic observations of high resolution with high signal-to-noise ($S/N$) are necessary to accurately determine the metallicity distribution.

To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($R = 25,000$) spectra with modest $S/N$ ($\sim$30 pixel$^{-1}$) for six Aquarius stream stars. Their data indicate a very narrow metallicity distribution: $\mbox{[Fe/H]} = -1.09 \pm 0.10$\,dex extending between $\mbox{[Fe/H]} = -1.25$ to $-0.98$\,dex. The largest [Fe/H] discrepancy between the two studies was $\Delta\mbox{[Fe/H]} = -0.66$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample. The most metal-poor star in the \citet{williams;et-al_2011} study was not observed by \citet{wylie-de-boer;et-al_2012}. The negligible level of chemical scatter observed in the \citet{wylie-de-boer;et-al_2012} sample is typical of what is found in globular or open clusters.

In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured light element abundances for the Aquarius stream stars -- the only study to do so until now. Their study primarily focussed on light elemental abundances: Na, O, Ni, Mg, and Al. Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars. Thus, by observing the abundances of light elements in stars that formed together, we can infer the star-formation history and environment. More specifically, an anti-correlation in sodium and oxygen abundance has been identified in all well-studied globular clusters to date. Originally this was thought to arise from internal mixing along the giant branch. However, dwarf stars were found to exhibit strong Na-enhancement and O-depletions, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing. It is well known now that photospheric abundance variations resulting from internal mixing are limited to C, N and Li. While the exact astrophysical mechanism for oxygen-depletion remains under debate, the chemical relationship is well-established empirically. The Na-O pattern provides the best chemical evidence that their chemical enrichment history has been dominated by Sn \textsc{ii} events and that those stars formed in a globular cluster-like environment.

From high-resolution spectroscopy of five stars in Aquarius, four of which had Na and O measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity. However, no strong oxygen depletion was evident in their data.

There are other chemical abundance patterns that allow us to infer the chemical evolution of a given cluster. \citet{nissen;schuster_1997} first noted that distant solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe]. \citet{fulbright_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient. If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{nissen;schuster_1997} proposed that this chemical trend may be indicative of the halo merger history since stars at larger $R_\odot$ are more likely to have been accreted rather than formed in-situ. \citet{wylie-de-boer;et-al_2012} found all the Aquarius stars in their sample to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dSph satellite. This provided an additional indication that the Aquarius stream stars originated in a globular cluster-like environment.

Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream must be the result of a tidally disrupted globular cluster. \citet{williams;et-al_2011} had previously precluded this possibility with any known globular clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{hel}$ with known, nearby globular clusters of similar metallicities. No known globular cluster could match their simulation.

We seek to investigate the nature of the Aquarius stream, specifically the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}. We present a detailed analysis for five  Aquarius stream members from high-resolution, high $S/N$ observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} on the Magellan Clay telescope. Details of the observations and data reduction are outlined in the following section. The data analysis is chronicalled in Section \ref{sec:analysis} and a detailed discussion of these results resides in Section \ref{sec:discussion}. In Section \ref{sec:conclusion} we present our conclusions and critical interpretations.

@@

\section{Observations \& Data Reduction}

The most complete sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}. Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional star from the original \citet{williams;et-al_2011} sample. The additional candidate, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined. All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and X additional standard stars were observed in March 2011. All observations were taken using a 1.0'' slit, providing a spectral resolution of $R = 28,000$ in the blue and $R = XX,XXX$ in the red arm. The total exposure times for our program stars varied per star from X-Y seconds to ensure a Signal-to-Noise ratio (S/N) in excess of 100 per pixel element at 600 nm.

Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration. The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}. One of our standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}. The resultant spectra from both reduction approaches were compared for residual fringing, S/N, and wavelength calibration. No noteworthy differences were present, and thus the CarPy pipeline was utilized for the remainder of the reductions. Each reduced echelle order was carefully normalized using a third order spline. Normalized orders   were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.

The white dwarf HR 6141 was observed on X with a S/N of 400 pixel$^{-1}$ as a telluric standard. The $S/N$ ratio for HR 6141 exceeds the $S/N$ ratio in any of our program stars. Although the atmospheric conditions at Las Campanas Observatory are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption. Critical transitions necessary for abundance analyses that are affected by the earth's atmosphere are corrected for telluric absorption (see \S\ref{sec:telluric-absorption}).

@@

\subsection{Radial Velocities}
\label{sec:radial-velocities}
The radial velocity for each star was determined in a two-step method. An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant star with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}. The observed spectrum was shifted to the pseudo-rest frame using this initial velocity estimate. Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.

With our spectra at near-rest, we measured the equivalent widths of $\sim$200 lines by automatically fitting Gaussian functions to the absorption profiles (see Section \ref{sec:line-measurements}). Fitted Gaussian profiles provide us with a measured equivalent width, the full-width half-maximum and the central wavelength of the profile. Thus, the residual radial velocity can be found from the ratio of the central and rest line wavelengths. The final radial velocity for the star is provided by the initial velocity and the mean of $\sim$200 residual line velocity measurements. Figure \ref{fig:line-velocities} shows the line velocities for HD41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$. As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and the standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements. This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$. This process was performed for all observations. The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method. Heliocentric velocities agree quite well with the \citet{williams;et-al_2011} published values: the mean absolute offset is $\langle\Delta{V_{hel}}\rangle = 2.8$\,km\,s$^{-1}$, demonstrating the accuracy of the velocities published by the RAVE survey.

@@

For the measurement of atomic absorption lines, we employed the line list of \citet{yong;et-al_2005} with additional transitions of Cr, Sc, Zn, and Sr from \citet{frebel;et-al_2010}. The line list was augmented with hyperfine-structure data for Sc and Mn from the Kurucz compilation \citet{kurucz;1998}. Molecular line data for CH was taken from \citet{plez;et-al_2008,plez;et-al_2009}. For lines with hyperfine structure, blended transitions or molecular features, we determined the abundance using a spectral synthesis approach. For all other transitions, equivalent widths were measured to determine the abundance.

The equivalent widths for all absorption lines were measured automatically using software written for this study. Given the rest wavelength and an initial guess of the full-width half-maxium (FWHM), a Gaussian function is iteratively fitted to the absorption profile. At the same time, the local continuum is found within 20\,\AA{} either side of the rest wavelength using a second-order polynomial. Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements. When determining the local continua, any neighbouring group of pixels that deviate significantly ($>$2-$\sigma$) from the local continua either belong to a persistent cosmic ray hit, or they are trough points of a neighbouring absorption profile. We attempt to fit a Gaussian profile to each group of deviating pixels, using the current best estimate for the local continuum. If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, we assume the outlier points belong to an absorption profile and all points belonging to that profile are excluded from the continuum determination.

When fitting Gaussian profiles, the $\chi^2$ difference between the observed spectra and the fitted profile is minimized. In order to account for crowded absorption regions, where the $\chi^2$ value might be influenced by a nearby profile, our $\chi^2$ function is weighted based on the distance to the rest wavelength by the function

@@

\noindent where the rest wavelength ($\lambda_{r}$) and FWHM ($\sigma$) are free parameters in the iterative fitting process. As a consequence of Eq. \ref{eq:chi-weight}, pixels near the rest wavelength are weighted higher than those on the wings, forcing the fitting scheme to disregard blended or crowded regions. Although this approach relies on a reasonably accurate radial velocity correction ($<$4\,km s$^{-1}$; which is easily achieved), it greatly improves the accuracy and robustness of the equivalent width measurements.

The results of our iterative Gaussian fitting approach are completely \textit{insensitive} to the initial FWHM guess. Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- which are unphysically large values for high-resolution spectra -- does not alter either the FWHM or the equivalent width for any of our measurements. Only a small increase in computational cost is observed. Although we are extremely confident in our automatic equivalent width measurements, every absorption profile was examined by eye for quality, and spurious measurements were excluded.

We list the atomic data and measured equivalent widths for atomic lines used during this analysis in Table \ref{tab:equivalent-widths}. Saturated lines were excluded by removing measurements with reduced equivalent widths, $\log_{10}{(EW/\lambda)} > -4.5$\, dex. A minimum detectable equivalent width was calculated as a function of wavelength based on the $S/N$, and only lines that exceeded a 3-$\sigma$ detection significance were included. We have verified the approach by comparing our measurements of 156 lines in HD 140283 with the study of \citet{norris;et-al_1996}. We only included measurements in the \citet{norris;et-al_1996} study that were not marked with line quality parameters. Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}. The mean difference is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present. We note that the scatter may  be directly attributed to the observed $S/N$, as other studies using the same equivalent width measurement software described here find better agreement with hand measurements for spectra with higher $S/N$ ($0.20 \pm 0.16$\,m{\AA} with $S/N \sim X$, $0.25 \pm 0.28$\,m{\AA} with $S/N \sim{} Y$; \citet{frebel;et-al_2013}).
